A Detection of the Environmental Dependence of the Sizes and Stellar Haloes of Massive Central Galaxies

### 2017-07-26 draft/paper2_v3.tex
Edit result 2

        \item Finally, the differences between the two sets of profiles becomes 
            more prominent at higher \mtot{}. 
            This can be seen further dividing the sample into two \mtot{} bins 
            (see Fig~\ref{fig:prof_2} and discussion in Appendix~\ref{app:robust}) 
            and when we discuss the relation between \mtot{} and 
            \minn{} (see Fig~\ref{fig:scaling_relation}). 
            This trend has potentially interesting implications

            \alexie{can we explain in one phrase?} that will be investigated in follow-up work.

@@

%This may explain why previous attempts to detect this signal using 
            %shallower images were not successful. 
\alexie{lets chat about the following two paragraphs}
    Generally speaking, such subtle environmental dependence of \mden{} profiles in 
    the \mtot{}-matched samples suggests that environment does not play a major role 
    in shaping massive galaxies \textbf{at fixed ``total'' stellar mass}.
    Therefore it is interesting to ask, for massive galaxies that \textbf{contain 
    similar \mstar{} in the \textit{in situ} component}, how does environment affect 
    their subsequent mass assembly?
    Assuming \minn{} is reasonable tracer of the \textit{in situ} mass, we compare the 
    \mden{} profiles of \minn{}-matched samples (right panel of Fig~\ref{fig:prof_1}).  
    Although the median \mden{} profiles are very similar at $R \leq 10$ kpc, the
    massive central galaxies in more massive haloes host much more prominent outer 
    stellar halo.

@@

    The previous section showed that the \mden{} profiles of massive galaxies show a dependence on the dark matter mass of their host halos. In this section, we now turn our attention to the more commonly studied mass size relation  (\mstar{}--$R_{\mathrm{e}}$). In addition, we will also consider halo mass dependence in the \mtot{}--\minn{} plane.

@@

    The tight relation between \mstar{} and effective radius (or half-light radius; 
    $R_{\mathrm{e}}$ or $R_{\mathrm{50}}$; e.g. \citealt{Shankar2013, Leja2013, 
    vdWel2014}) is one of the most important scaling relation for ETGs. 
    Despite numerous attempts, previous studies have failed to detect the dark matter halo mass dependence of the \mstar{}--$R_{\mathrm{e}}$ relation at low-$z$ 
    (e.g. \citealt{Weinmann2009, Nair2010, HCompany13, Cerbrian2014}; 
    but see \citealt{Yoon2017}).

    The previous section clearly showed that the profiles of massive galaxies depend on the masses of their host dark matter halos. We now ask whether or not this dependence is also manifest when considered in terms of the more traditionally studied \mstar{}--$R_{\mathrm{e}}$ relation. However, when considering the mass-size relation, there is ambiguity and multiple approaches in terms of defining "sizes". This is especially true in the context of massive galaxies with extended stellar haloes (a reason why we prefer to show profiles directly as in the previous section). In this section, we still use \mtot{} as proxy of ``total'' \mstar{} and we adopt 
    the radius enclosing 50\% of luminosity \alexie{mass?} within 100 kpc ($R_{\mathrm{50}}$; derived 
    from the $i$-band curve-of-growth) as the ``size''. This definition of ``effective radius'' is more robust against structural details, 
    choice of model, and the background subtraction \alexie{compared to what?}. 
    Massive galaxies from this sample are large enough that the impact of seeing is not a concern.

@@

@@

%% ------------------------------------------------------------------------------------ %% 
\section{A. Basic Statistical Properties of the Sample} 
	\label{app:basic}

@@

@@

%% ------------------------------------------------------------------------------------ %% 
\section{B. Comparisons of \mden{} profiles in different redshift bins}
    \label{app:redshift}

@@

@@

@@

%% ------------------------------------------------------------------------------------ %% 
\section{C. Match the \rbcg{} and \nbcg{} samples in \mstar{} and redshift distributions}
    \label{app:match}

%% ------------------------------------------------------------------------------------ %% 
\section{D. Robustness of the \mden{} Differences} 
	\label{app:robust}

@@

%% ------------------------------------------------------------------------------------ %% 
\section{E. Stellar Mass Curve-of-Growth for Massive Central Galaxies} 
	\label{app:cog}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\section{F. Comparison of \mden{} profiles using \mstar{} from the GAMA survey}
    \label{app:gama}

>>>>

        \item Finally, the differences between the two sets of profiles becomes 
            more prominent at higher \mtot{}. 
            This can be seen further dividing the sample into two \mtot{} bins 
            (see Fig~\ref{fig:prof_2} and discussion in Appendix~\ref{app:robust}) 
            and when we discuss the relation between \mtot{} and 
            \minn{} (see Fig~\ref{fig:scaling_relation}). 
            This trend potentially indicates that the assembly of stellar haloes in 
            more massive central galaxies become more sensitive to their 
            environments or halo mass.

@@

%This may explain why previous attempts to detect this signal using 
            %shallower images were not successful.

    Generally speaking, such subtle environmental dependence of \mden{} profiles in 
    the \mtot{}-matched samples suggests that environment does not play a major role 
    in shaping massive galaxies \textbf{at fixed ``total'' stellar mass}.
    Therefore it is interesting to ask, for massive galaxies that \textbf{contain 
    similar \mstar{} in the \textit{in situ} component}, how does environment affect 
    their subsequent mass assembly?
    Assuming \minn{} is reasonable tracer of the \textit{in situ} mass, we compare the 
    \mden{} profiles of \minn{}-matched samples (right panel of Fig~\ref{fig:prof_1}).  
    Although the median \mden{} profiles are very similar at $R \leq 10$ kpc, the
    massive central galaxies in more massive haloes host much more prominent outer 
    stellar halo.

@@

    The above section shows that the \mden{} profiles of massive galaxies show a 
    dependence on the masses of their host dark matter haloes. 
    In this section, we now turn our attention to the more commonly studied stellar 
    mass--size relation (\mstar{}--$R_{\mathrm{e}}$). 
    In addition, we will also consider halo mass dependence on the 
    \mtot{}--\minn{} plane.

@@

    The tight relation between \mstar{} and effective radius (or half-light radius; 
    $R_{\mathrm{e}}$ or $R_{\mathrm{50}}$; e.g. \citealt{Shankar2013, Leja2013, 
    vdWel2014}) is one of the most important scaling relation for ETGs. 
    Despite numerous attempts, previous studies have failed to detect the 
    \mhalo{}--dependence of the \mstar{}--$R_{\mathrm{e}}$ relation at low-$z$ 
    (e.g. \citealt{Weinmann2009, Nair2010, HCompany13, Cerbrian2014}; 
    except for recent result by \citealt{Yoon2017}).

    The previous section clearly showed that the \mden{} profiles of massive central 
    galaxies depend on the masses of their host dark matter halos. 
    We now ask whether or not this dependence is also manifest when considered in 
    terms of the more traditionally studied \mstar{}--$R_{\mathrm{e}}$ relation. 
    However, when considering the mass-size relation, there is ambiguity and there are
    multiple approaches to define ``sizes''. 
    This is especially relevant in the context of massive galaxies with extended 
    stellar haloes (a reason why we prefer to show \mden{} profiles directly as in 
    the previous section). 
    In this section, we still use \mtot{} as proxy of ``total'' \mstar{} and we adopt 
    the radius enclosing 50\% of stellar mass within 100 kpc ($R_{\mathrm{50}}$; 
    derived from the $i$-band curve-of-growth) as the ``size''. 
    This definition of ``effective radius'' is more robust against structural details, 
    choice of model, and the background subtraction comparing to the effective radius 
    estimated by simple 2-D modeling method (e.g. single-\ser{} model). 
    Massive galaxies from this sample are large enough that the impact of seeing is 
    not a concern.

@@

%% ------------------------------------------------------------------------------------ %% 
\section{Basic Statistical Properties of the Sample} 
	\label{app:basic}

@@

@@

%% ------------------------------------------------------------------------------------ %% 
\section{Comparisons of \mden{} profiles in different redshift bins}
    \label{app:redshift}

@@

@@

%% ------------------------------------------------------------------------------------ %% 
\section{Match the \rbcg{} and \nbcg{} samples in \mstar{} and redshift distributions}
    \label{app:match}

@@

%% ------------------------------------------------------------------------------------ %% 
\section{Robustness of the \mden{} Differences} 
	\label{app:robust}

@@

@@

%% ------------------------------------------------------------------------------------ %% 
\section{Stellar Mass Curve-of-Growth for Massive Central Galaxies} 
	\label{app:cog}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\section{Comparison of \mden{} profiles using \mstar{} from the GAMA survey}
    \label{app:gama}
